

```{r}
library(data.table)
library(stats)
library(dplyr)
library(lmtest)
library(zoo)
library(sandwich)
install.packages("AER")
library(survival)
library(AER)
getwd()
setwd("C:/Users/jiaji/Downloads/")
```

#question5
```{r}
smoking <- read.csv('Smoking.csv',header = TRUE)
head(smoking)
length(smoking)
dim(smoking)[1]
```

```{r}
#a
prob_smoking_all_worker=dim(smoking[smoking$smoker==1,])[1]/dim(smoking)[1]
prob_smoking_bans=dim(smoking[smoking$smoker==1|smoking$smkban==1,])[1]/dim(smoking)[1]
prob_smoking_not_bans=dim(smoking[smoking$smoker==1|smoking$smkban==0,])[1]/dim(smoking)[1]
#b
reg_11.1 <- lm(smoker ~ smkban, data = smoking)
summary(reg_11.1)
```
#the difference is -0.078 with a standard error of 0.009.The resulting t-statistic is -8.66,so the coefficient is statistically significant.

```{r}
#c
smoking=smoking%>%mutate(age2=age^2)
reg_11.2 <- lm(smoker ~ smkban + female + age + age2+hsdrop+hsgrad+colsome+colgrad+black+hispanic,data = smoking)
summary(reg_11.2)
```
#the difference is -0.047,smaller than the effect in b.Thus,b suffers from ommitted variables.We conclude that smoking may be correlated with 
#the education/race/gender indicators or with age.For example,
#workers with a college degree are more likely to work in an office with a smoking
#ban than high-school dropouts, and college graduates are less likely to smoke than
#high-school dropouts.

```{r}
#d
coeftest(reg_11.2, vcov = vcovHC(reg_11.2, type = "HC1"))
#The t-statistic is -5.27, so the coefficient is statistically significant at the 1% level.
```
```{r}
#e
coeftest(reg_11.2, vcov = vcovHC(reg_11.2, type = "HC1"))
#The omitted education status is “Masters degree or higher.” Thus the coefficients show the
#increase in probability relative to someone with a postgraduate degree.
#the coefficient on Colgrad is 0.045, so the probability of smoking for a college
#graduate is 0.045 (4.5%) higher than for someone with a postgraduate degree.
#Similarly, the coefficient on HSdrop is 0.323, so the probability of smoking for a
#college graduate is 0.323 (32.3%) higher than for someone with a postgraduate
#degree. Because the coefficients are all positive and get smaller as educational
#attainment increases, the probability of smoking falls as educational attainment
#increases.
```
```{r}
#f
reg_11.3 <- glm(smoker ~ smkban + female + age + age2+hsdrop+hsgrad+colsome+colgrad+black+hispanic,data = smoking,family = binomial(link = "probit"))
summary(reg_11.3)
coeftest(reg_11.3, vcov = vcovHC(reg_11.3, type = "HC1"))
#The t-statistic for the coefficient on smkban is -5.43, very similar to the value for the linear probability model. The F-statistic is
#significant at the 1% level, as in the linear probability model.
```
```{r}
#g
reg_11.4 <- glm(smoker ~ smkban + female + age + age2 +hsdrop+hsgrad+colsome+colgrad+black+hispanic,data = smoking,family = binomial(link = "logit"))
summary(reg_11.4)
coeftest(reg_11.4, vcov = vcovHC(reg_11.4, type = "HC1"))
#The t-statistic for the coefficient on smkban
#is -5.29, very similar to the value for the linear probability and probit models. The Fstatistic
#is significant at the 1% level, as in the linear probability model.
```
```{r}
#h.i
temp.data = data.frame(female=0,age2=20^2,age=20,hispanic=0,hsdrop=1,smkban=0,black=0,hsgrad=0,colsome=0,colgrad=0)
logit.11.3.predict <- as.data.frame(predict(reg_11.3, newdata = temp.data, 
                                            type = "response", se=TRUE))
#h.ii
temp.data = data.frame(female=1,age2=40^2,age=40,hispanic=0,hsdrop=0,smkban=0,black=1,hsgrad=0,colsome=0,colgrad=1)
logit.11.4.predict <- as.data.frame(predict(reg_11.3, newdata = temp.data, 
                                            type = "response", se=TRUE))
#h.iii
temp.data = data.frame(female=0,age2=20^2,age=20,hispanic=0,hsdrop=1,smkban=0,black=0,hsgrad=0,colsome=0,colgrad=0)
logit.11.5.predict <- as.data.frame(predict(reg_11.2, newdata = temp.data, 
                                            type = "response", se=TRUE))
temp.data = data.frame(female=1,age2=40^2,age=40,hispanic=0,hsdrop=0,smkban=0,black=1,hsgrad=0,colsome=0,colgrad=1)
logit.11.6.predict <- as.data.frame(predict(reg_11.2, newdata = temp.data, 
                                            type = "response", se=TRUE))
#h.iv
#The linear probability model assumes that the marginal impact of workplace smoking
#bans on the probability of an individual smoking is not dependent on the other
#characteristics of the individual. On the other hand, the probit and logit models’ predicted
#marginal impact of workplace smoking bans on the probability of smoking depends on
#individual characteristics. Therefore, in the linear probability model, the marginal impact
#of workplace smoking bans is the same for Mr. A and Mr. B, although their profiles
#would suggest that Mr. A has a higher probability of smoking based on his
#characteristics.
```
#question6
```{r}
#a.i
movies <- read.csv('movies.csv',header = TRUE)
head(movies)

ln_reg=lm(log10(assaults)~year1 +year2 +year3 +year4 +year5 +year6 +year7 +year8 +year9 +year10 +month1 +month2 +month3 +month4 +month5 +month6 +month7 +month8
          +month9 +month10 +month11 +month12,data =movies )
summary(ln_reg)
coeftest(ln_reg, vcov = vcovHC(ln_reg, type = "HC1"))
#there is evidence of seasonality in assaults.There is tend to be more assaults in
#some months like month5 and month9 than others.
```
```{r}
#a.ii
movies=movies%>%mutate(attend=attend_v + attend_m +
                  attend_n)
ln_reg.1=lm(attend~year1 +year2 +year3 +year4 +year5 +year6 +year7 +year8 +year9 +year10 +month1 +month2 +month3 +month4 +month5 +month6 +month7 +month8
          +month9 +month10 +month11 +month12,data =movies )
summary(ln_reg.1)
coeftest(ln_reg, vcov = vcovHC(ln_reg.1, type = "HC1"))
#There is evidence of seasonality in movie attendance.There is tend to be more attendance in
#some months than others.
```
```{r}
#b.i

ln_reg.2=lm(log10(assaults)~attend_v + attend_m +
            attend_n+year1 +year2 +year3 +year4 +year5 +year6 +year7 +year8 +year9 +year10 +month1 +month2 +month3 +month4 +month5 +month6 +month7 +month8
          +month9 +month10 +month11 +month12+
            h_chris+h_newyr +h_easter +h_july4 +h_mem +h_labor +w_maxa +w_maxb +w_maxc+w_mina +w_minb +w_minc +w_rain,data =movies )
summary(ln_reg.2)
coeftest(ln_reg.2, vcov = vcovHC(ln_reg.2, type = "HC1"))

#Based on the regression, viewing a strongly violent movie
#increase assaults.It is the estimated
#effect statistically significant.
```
```{r}
#b.ii
#attendance at strongly violent movies affect assaults differently
#than attendance at moderately violent movies.Differently
#attendance at nonviolent,because the coefficients for all of these variables are different.

#b.iii
predict_change= ln_reg.2$coefficients[1]+ln_reg.2$coefficients[2]*6000000-ln_reg.2$coefficients[3]*2000000-ln_reg.2$coefficients[4]*1000000
```
```{r}
#c
reg15 = ivreg(log(assaults)~attend_v+attend_m+attend_n+year1+year2+year3+year4+year5+year6+year7+year8+year9+month1+month2+month3+month4+month5+month6+month7+month8+month9+month10+month11+h_chris+h_newyr+h_easter+h_july4+h_mem+h_labor+w_maxa+w_maxb+w_maxc+w_mina+w_minb+w_minc+w_rain+w_snow|year1+year2+year3+year4+year5+year6+year7+year8+year9+month1+month2+month3+month4+month5+month6+month7+month8+month9+month10+month11+h_chris+h_newyr+h_easter+h_july4+h_mem+h_labor+w_maxa+w_maxb+w_maxc+w_mina+w_minb+w_minc+w_rain+w_snow+pr_attend_v+pr_attend_m+pr_attend_n, data = movies)
summary(reg15)
coeftest(reg15, vcov = vcovHC(reg15, type = "HC1"))
#Based on the regression, viewing a strongly violent movie
#increase assaults.It is the estimated
#effect statistically significant.The t-value for attend_v is -3.590,F-statistic is less than 1.96,The F-statistic is
#significant at the 1% level.
#attendance at strongly violent movies affect assaults is not so differently
#than attendance at moderately violent movies,
#because the coefficients for all of these variables are different but the differences are not too much
predict_change= reg15$coefficients[1]+reg15$coefficients[2]*6000000-reg15$coefficients[3]*2000000-reg15$coefficients[4]*1000000
#the predicted effect on assaults will decrease 12975.24
```
```{r}
#d
reg15.1 = ivreg(log(assaults)~attend_v+attend_m+attend_n+year1+year2+year3+year4+year5+year6+year7+year8+year9+month1+month2+month3+month4+month5+month6+month7+month8+month9+month10+month11+h_chris+h_newyr+h_easter+h_july4+h_mem+h_labor+w_maxa+w_maxb+w_maxc+w_mina+w_minb+w_minc+w_rain+w_snow|year1+year2+year3+year4+year5+year6+year7+year8+year9+month1+month2+month3+month4+month5+month6+month7+month8+month9+month10+month11+h_chris+h_newyr+h_easter+h_july4+h_mem+h_labor+w_maxa+w_maxb+w_maxc+w_mina+w_minb+w_minc+w_rain+w_snow+attend_v_f+attend_m_f+attend_n_f+attend_v_b+attend_m_b+attend_n_b+pr_attend_v+pr_attend_m+pr_attend_n, data = movies)
summary(reg15.1)
coeftest(reg15, vcov = vcovHC(reg15.1, type = "HC1"))
coeftest(reg15, vcov = vcovHC(reg15, type = "HC1"))
#Based on the regression, viewing a strongly violent movie
#increase assaults.It is the estimated
#effect statistically significant.The t-value for attend_v is -3.590,F-statistic is less than 1.96,The F-statistic is
#significant at the 1% level.
#attendance at strongly violent movies affect assaults is not so differently
#than attendance at moderately violent movies,
#because the coefficients for all of these variables are different but the differences are not too much
predict_change= reg15$coefficients[1]+reg15$coefficients[2]*6000000-reg15$coefficients[3]*2000000-reg15$coefficients[4]*1000000
#the predicted effect on assaults will decrease 12975.24
```
```{r}
#e
## get J-statistics
reg16 =lm(residuals(reg15)~year1+year2+year3+year4+year5+year6+year7+year8+year9+month1+month2+month3+month4+month5+month6+month7+month8+month9+month10+month11+h_chris+h_newyr+h_easter+h_july4+h_mem+h_labor+w_maxa+w_maxb+w_maxc+w_mina+w_minb+w_minc+w_rain+w_snow+attend_v_f+attend_m_f+attend_n_f+attend_v_b+attend_m_b+attend_n_b+pr_attend_v+pr_attend_m+pr_attend_n, data=movies)
summary(reg16)

linearHypothesis(reg16, c("attend_v_f", "attend_m_f","attend_n_f", "attend_v_b","attend_m_b","attend_n_b", "pr_attend_v", "pr_attend_m", "pr_attend_n"),test="Chisq")
#Because p-value>0.05,thus the instruments are valid.
```

#f
#I conclude that violent movies are affected by many factors, such as weather, assults, season and so on.The coefficients of 
#different months differ a lot. Thus,the time effect of violent movies cannot be ignored.As the increase in the violent movies,
#the increase in short-term violent behaviour.